### 2023-01-12 Manuscript/Draft1.Rmd
fairly minor paper updates

```{r strata-plot, echo=FALSE,out.width="95%",fig.show='hold', fig.align='center', fig.cap="Strata inhabited by each species in our population models."}
knitr::include_graphics(c("Images/Strata.png"))
```

>>>>

```{r strata-plot, echo=FALSE,out.width="95%",fig.show='hold', fig.align='center', fig.cap="Strata inhabited by each species in our population models."}
knitr::include_graphics(c("Images/Strata.png"))
knitr::include_graphics(c("Images/Excluded_strata.png"))
```
